---
title: "Introduction to toolPhD"
author: 'Tien-Cheng Wang'
date: "`r Sys.Date()`"
output:
  pdf_document:
    fig_caption: no
    toc: no
  html_document:
    df_print: paged
    toc: yes
vignette: >
  %\VignetteIndexEntry{Introduction to toolPhD}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
csl: https://tinyurl.com/apa6-meta-analysis
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr);suppressWarnings(library(dplyr));
suppressWarnings(library(ggplot2));library(tidyr);
library(kableExtra);library(knitr);library(purrr)
options(dplyr.summarise.inform = FALSE)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview


The package `toolPhD` is part of the journey aside from publication works of PhD. The package is a collection of functions which the author find useful and hopefully also for you.


The goal of this vignette is to introduce users to these functions and get started in analyzing dataset with ease and comfortation. 

Further analysis for original publication using this package can be found in the link ( [click](https://github.com/Illustratien/Wang_2023_TAAG)).

## Installation
The package can be installed using the following functions:

```{r, eval=FALSE}
# Install from CRAN, release soon
# install.packages('toolPhD', dependencies=TRUE)

# Install development version from Github
devtools::install_github("Illustratien/toolPhD")

```

Then the package can be loaded using the function
```{r}
library(toolPhD)
```



## Structure overview of toolPhD

toolPhD contains different functions to calculate stability indices, including:

1.  over view of data frame
2.  round scale 
\clearpage

<!-- ## Build-in data set -->

<!-- The default data set `Data` is the subset of $APSIM$ simulated wheat data set, which includes 5 genotypes in 4 locations for 4 years, with 2 nitrogen application rates, 2 sowing dates, and 2 $CO_2$ levels of treatments [@casadebaig2016]. Full dataset used in the publication see here [click](https://zenodo.org/record/4729636). -->

<!-- `Data` in this package is a data frame with 640 observations and 8 variables. -->

<!-- : Data Structure -->

<!-- | Parameters | Number | Description | -->
<!-- | :--- | ---: | :--- | -->
<!-- | Trait |   | Wheat yield ($kg~ha^{-1}$).|  -->
<!-- | Genotype | 5 | varieties.| -->
<!-- | Environment | 128 | unique combination of environments for each genotype.| -->
<!-- | Year | 4 | years.| -->
<!-- | Sites | 4 | locations.| -->
<!-- | Nitrogen | 2 | nitrogen application levels.| -->
<!-- | $CO_2$ | 2 | $CO_2$ concentration levels.| -->
<!-- | Sowing | 2 | sowing dates.| -->

\clearpage

## Examples
```{r}
rm(list=ls())
library(toolPhD)
### load data

dplyr::glimpse(iris)
view_df(iris)
```
\clearpage


\newpage
## Citing `toolPhD`
Wang, TC.ToolPhD: get your PhD smoother.

